---
title: "TS_nonlinear_analysis"
author: "Christian Rohrsen"
date: "6 Dezember 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

For the first time
```{r cars}
install.packages("nonlinearTseries")
install.packages("signal")
```

If you did not do so yet, set the right working directory
```{r cars}

setwd("C:/Users/chise/Downloads/TS-nonlinear-analysis-master/TS-nonlinear-analysis-master")
```

Source the script with the functions and packages needed for analysis
```{r cars}

source("StrokePrepFunctions.R")
require(nonlinearTseries)
require(signal)

```

Read the fly flight data and filter out the noise
```{r cars}

  #flyTraces <- flyDataImport()
  
  flyTraces$Trace<- flyTraces$Right-flyTraces$Left
  
  plot(flyTraces$Trace,type="l")
  
  plot(diff(flyTraces$Time))

  flyTracesFiltered <- flyDataFilter(flyTraces, frequency = .12, order = 3)
  
  plot(flyTracesFiltered$Trace,type="l")
  
```

This function estimates an appropiate time lag by using the autocorrelation function or the average mutual information .
```{r cars}
  
LAG <- timeLag(flyTracesFiltered$Trace, technique = "ami",selection.method = "first.e.decay",lag.max = 20, do.plot = TRUE)  
  
  use.ts<-diff(flyTracesFiltered$Trace)
  
LAG <- timeLag(use.ts, technique = "ami",selection.method = "first.e.decay",lag.max = 20, do.plot = TRUE)

```

This function determines the minimum embedding dimension from a scalar time series using the algorithm proposed by L. Cao
```{r cars}

emb.dim = estimateEmbeddingDim(use.ts, threshold = 0.95,
                                 time.lag = LAG, max.embedding.dim = 25)
```
The space time separation is a broadly-used method of detecting non-stationarity and temporal correlations in the time series being analyzed. The space time separation plot is also used to select a proper Theiler window by selecting a temporal separation enough to saturate the contour lines.
  

```{r cars}
  spaceTime = spaceTimePlot(time.series = use.ts,time.lag = LAG,
                            embedding.dim = emb.dim,
                            number.time.steps = 40,type="b")
  

  theilerw = 30
```

Functions for estimating the correlation sum and the correlation dimension of a dynamical system from 1-dimensional time series using Takens' vectors.

```{r cars}
corr.dim =  corrDim(use.ts, min.embedding.dim = emb.dim, 
                      max.embedding.dim = emb.dim + 7,
                      time.lag = LAG,
                      min.radius = 0.04, max.radius = (max(use.ts)-min(use.ts))/2, 
                      n.points.radius = 45, 
                      theiler.window = theilerw,
                      do.plot = TRUE)

```

Several chaotic invariants are estimated by using linear regression. This function provides a common interface for the estimate of all these parameters (see corrDim, dfa and maxLyapunov for examples)
  
```{r cars}
D<- estimate(corr.dim,regression.range = c(regression.range.min,regression.range.max),use.embeddings = use.embeddings.min:use.embeddings.max,do.plot = T)
```

Predict the future data from the library: the first half of the data
```{r cars}

message("please enter the radius")
radius = scan(n=1,what= numeric())
  
  # obtenemos predicciones para las proximas 500 (prediction.step) muestras basandonos
  #en las 4000 primeras muestras de x
  prediction = nonLinearPredict2(use.ts[1:round(length(use.ts)/2)], embedding.dim = emb.dim, time.lag = LAG, radius = c(0.01,radius),
                                  radius.increment = 0.02, prediction.step = 1:40)
  # comparamos... Fijate como la prediccion va empeorando a medida que pasa el tiempo. Esto
  # es tipico de sistemas no lineales
  
  plot(use.ts[(round(length(use.ts)/2)+1):(round(length(use.ts)/2)+40)], type = "l", ylim = range(use.ts[(round(length(use.ts)/2)+1):(round(length(use.ts)/2)+40)], Prediction))
  lines(prediction[,1], type = "l", col = 2)
  lines(prediction[,2], type = "l", col = 3)


```

```{r cars}
```

